---
title: "Basic text mining"
format: html
---

# Welcome to the tutorial!

In this tutorial, we'll use .txt version of the Svacchanda-Tantra downloaded from Göttingen Register of Electronic Texts in Indian Languages ([GRETIL](https://gretil.sub.uni-goettingen.de/gretil.html) - you can find the text under 'saiva' [here](https://gretil.sub.uni-goettingen.de/gretil.html#RLSaiva)).

## Reading in the libraries we need

```{r, include=FALSE}
library(tidyverse)
library(writexl)
```

## Read in the text

We'll use the function `read_lines` to read in the txt file line-by-line, and we save it in `text_raw`.

The `|>` means 'do this next'.
So after we've read the line by line, we'll put it in a spreadsheet-like format called a 'tibble', using the `as_tibble` function.

We save the result of these operations in a new variable we call `text_raw`

```{r}
text_raw = read_lines("data/sa_svacchandatantra.txt") |> 
  as_tibble()
```

## Clean the text

Let's have a look by just typing the name of the variable:

```{r}
text_raw
```

### Removing empty lines

All of the lines that were empty have an empty row in our variable.
Let's remove them using the `filter` function which selects rows based on some condition.

```{r}
text_drop_empty_lines = text_raw |> 
  filter(value != "")

text_drop_empty_lines
```

Great, we're now down to 7,431 rows from 11,160!

### Selecting only the lines that we care about

We notice that the text only begins after the line with the text "\# Text".
That's in row 43.

Let's use the `slice` function to select just rows from row 44 until the end ('n()' gives us the total number of rows).

```{r}
relevant_text <- text_drop_empty_lines |> 
  slice(44:n())
```

## Save out the text

We'll save out the text as an excel file:

```{r}
write_xlsx(relevant_text, "data/gretil_example.xlsx")
```
